TBD

### 2021-02-19 outputs/paper/paper.Rmd
t-test tables formatted

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(kableExtra)
library(janitor)
library(dplyr)
library(palettetown)
library(wesanderson)
library(RColorBrewer)
library(ggthemes)
library(scales)
library(broom)

@@

# Q5
control_q5 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q5)
treatment_q5 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q5)
t.test(control_q5, treatment_q5)

#Q6
control_q6 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q6)
treatment_q6 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q6)
t.test(control_q6, treatment_q6)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(kableExtra)
library(janitor)
library(dplyr)
library(palettetown)
library(wesanderson)
library(RColorBrewer)
library(ggthemes)
library(scales)
library(broom)
library(purrr)

@@

#Q5
control_q5 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q5)
treatment_q5 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q5)
t3 <- t.test(control_q5, treatment_q5)

#Q6
control_q6 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q6)
treatment_q6 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q6)
t4 <- t.test(control_q6, treatment_q6)

#Q5 + Q6 compiled t-test table
t_tests <- map_df(list(t3, t4), tidy)
t_tests = subset(t_tests, select = -c(alternative, method))
t_tests %>%  
  kable(
    col.names = c("Mean Difference",
                  "Mean (Employees Before Intervention)",
                  "Mean (Employees Post-Intervention)",
                  "t",
                  "p",
                  "df",
                  "Low",
                  "High")

  ) %>%
  add_header_above(c(" ", "Control" = 1, "Treated" = 1, " ", " ", " ", "Confidence" = 2)) %>%
  kable_paper(c("striped", "hover")) %>%
  landscape()
